---
title: "Social Networks and Mental Diseases"
author: "Simone Di Cicco"
date: "8/4/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Social Networks and Metal Diseases"
output: html_notebook
---

## Codebook

### Introduction

### Dataset source

The dataset has been gathered from IHME (Institute for Health Metrics and Evaluation). This organization is reachable by the website http://www.healthdata.org. They provides absolutely open and filterable data. The tool is available at the following link:
- http://ghdx.healthdata.org/gbd-results-tool

The dataset I extracted is available at the following link. The status of the dataset you are downloading is intact. You will manage and/or explore the dataset before any cleaning/processing:
- Link at the dataset.

### R Application

Also the R application I coded to gain the result is absolutely open and available on GitHub:
- https://github.com/ukaoskid/ihme-social-networks

### Dataset field meaning

#### Location (id, name)
- 10, Cambodia
- 101, Canada
- 102, United States
- 105, Antigua and Barbuda
- 106, The Bahamas
- 107, Barbados
- 108, Belize
- 109, Cuba
- 11, Indonesia
- 110, Dominica
- 111, Dominican Republic
- 112, Grenada
- 113, Guyana
- 114, Haiti
- 115, Jamaica
- 116, Saint Lucia
- 117, Saint Vincent and the Grenadines
- 118, Suriname
- 119, Trinidad and Tobago
- 12, Laos
- 121, Bolivia
- 122, Ecuador
- 123, Peru
- 125, Colombia
- 126, Costa Rica
- 127, El Salvador
- 128, Guatemala
- 129, Honduras
- 13, Malaysia
- 130, Mexico
- 131, Nicaragua
- 132, Panama
- 133, Venezuela
- 135, Brazil
- 136, Paraguay
- 139, Algeria
- 14, Maldives
- 140, Bahrain
- 141, Egypt
- 142, Iran
- 143, Iraq
- 144, Jordan
- 145, Kuwait
- 146, Lebanon
- 147, Libya
- 148, Morocco
- 149, Palestine
- 15, Myanmar
- 150, Oman
- 151, Qatar
- 152, Saudi Arabia
- 153, Syria
- 154, Tunisia
- 155, Turkey
- 156, United Arab Emirates
- 157, Yemen
- 16, Philippines
- 160, Afghanistan
- 161, Bangladesh
- 162, Bhutan
- 163, India
- 164, Nepal
- 165, Pakistan
- 168, Angola
- 169, Central African Republic
- 17, Sri Lanka
- 170, Congo
- 171, Democratic Republic of the Congo
- 172, Equatorial Guinea
- 173, Gabon
- 175, Burundi
- 176, Comoros
- 177, Djibouti
- 178, Eritrea
- 179, Ethiopia
- 18, Thailand
- 180, Kenya
- 181, Madagascar
- 182, Malawi
- 183, Mauritius
- 184, Mozambique
- 185, Rwanda
- 186, Seychelles
- 187, Somalia
- 189, Tanzania
- 19, Timor-Leste
- 190, Uganda
- 191, Zambia
- 193, Botswana
- 194, Lesotho
- 195, Namibia
- 196, South Africa
- 197, Swaziland
- 198, Zimbabwe
- 20, Vietnam
- 200, Benin
- 201, Burkina Faso
- 202, Cameroon
- 203, Cape Verde
- 204, Chad
- 205, Cote d'Ivoire
- 206, The Gambia
- 207, Ghana
- 208, Guinea
- 209, Guinea-Bissau
- 210, Liberia
- 211, Mali
- 212, Mauritania
- 213, Niger
- 214, Nigeria
- 215, Sao Tome and Principe
- 216, Senegal
- 217, Sierra Leone
- 218, Togo
- 22, Fiji
- 23, Kiribati
- 24, Marshall Islands
- 25, Federated States of Micronesia
- 26, Papua New Guinea
- 27, Samoa
- 28, Solomon Islands
- 29, Tonga
- 298, American Samoa
- 30, Vanuatu
- 305, Bermuda
- 33, Armenia
- 34, Azerbaijan
- 349, Greenland
- 35, Georgia
- 351, Guam
- 36, Kazakhstan
- 37, Kyrgyzstan
- 376, Northern Mariana Islands
- 38, Mongolia
- 385, Puerto Rico
- 39, Tajikistan
- 40, Turkmenistan
- 41, Uzbekistan
- 422, Virgin Islands, U.S.
- 43, Albania
- 433, Northern Ireland
- 434, Scotland
- 435, South Sudan
- 44, Bosnia and Herzegovina
- 45, Bulgaria
- 46, Croatia
- 4636, Wales
- 47, Czech Republic
- 4749, England
- 48, Hungary
- 49, Macedonia
- 50, Montenegro
- 51, Poland
- 52, Romania
- 522, Sudan
- 53, Serbia
- 54, Slovakia
- 55, Slovenia
- 57, Belarus
- 58, Estonia
- 59, Latvia
- 6, China
- 60, Lithuania
- 61, Moldova
- 62, Russia
- 63, Ukraine
- 66, Brunei
- 67, Japan
- 68, South Korea
- 69, Singapore
- 7, North Korea
- 71, Australia
- 72, New Zealand
- 74, Andorra
- 75, Austria
- 76, Belgium
- 77, Cyprus
- 78, Denmark
- 79, Finland
- 8, Taiwan
- 80, France
- 81, Germany
- 82, Greece
- 83, Iceland
- 84, Ireland
- 85, Israel
- 86, Italy
- 87, Luxembourg
- 88, Malta
- 89, Netherlands
- 90, Norway
- 91, Portugal
- 92, Spain
- 93, Sweden
- 94, Switzerland
- 97, Argentina
- 98, Chile
- 99, Uruguay

#### Measures (id, name, meaning):

- 6, Incident, Number of new cases in the population at a given time

#### Metric (id, name):
- 1, Number
- 2, Percentage
- 3, Rate

#### Diseases (id, name):

- 559, Schizophrenia
- 560, Alcohol use disorders
- 562, Opioid use disorders
- 563, Cocaine use disorders
- 564, Amphetamine use disorders
- 565, Cannabis use disorders
- 568, Major depressive disorder
- 569, Dysthymia
- 570, Bipolar disorder
- 571, Anxiety disorders
- 576, Autism
- 577, Asperger syndrome and other autistic spectrum disorders
- 578, Attention-deficit/hyperactivity disorder
- 579, Conduct disorder
- 582, Idiopathic developmental intellectual disability
- 585, Other mental and substance use disorders
- 566, Other drug use disorders

### Plots

```{r, echo = FALSE}

```

